Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-30 WRITEUP/ms.tex
checked sec 6.2

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than the Milky Way at 8\,kpc, but comparable to 
those observed in starburst galaxies and the nearby ULIRGs \citep{Boulares90a, Scoville91a, Weiss01a, Leroy15a}.
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

% The pressure of MCCs identified at the lowest $n_{\rm cut}$ ranges between $\log\left(P/K$\,\cc$\right)\in[6, 8.7]$, with a median of 7.4.
The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B)\in[7, 9]$\,K\,\cc, with a median of 7.6\,K\,\cc.
Such high pressure is comparable to those observed in local ultra-luminous IR galaxies (ULIRGs; 
e.g., \citealt{}); however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and 
molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based 
on spatially resolved CO line \obs.

@@

If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, due to energy dissipation on small-scales, such (sub-)structures are no longer supported by turbulence. 
This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Further, the SFR of \flower is very bursty and high SFR stages are only transient.
%
Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.

>>>>

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the LMC, but comparable to those observed in starburst galaxies and the nearby 
ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

% The pressure of MCCs identified at the lowest $n_{\rm cut}$ ranges between $\log\left(P/K$\,\cc$\right)\in[6, 8.7]$, with a median of 7.4.
The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B)\in[7, 9]$\,K\,\cc, with a median of 7.6\,K\,\cc.
Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and 
molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based 
on spatially resolved CO line \obs.

@@

If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. 
This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Further, the SFR of \flower is very bursty and high SFR stages are only transient.
%
Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
